Real-time Attention Assessment for Social Robots

### 2015-09-17 paper.tex
Added a paragraph mentioning no treatment of visual occlusions in focus of attention assessment

>>>>

Besides, our approach does not account for visual occlusions when computing the
focus of attention: any frame within the cone of the visual field of attention
is considered as \emph{in focus}. In reality, some of the frames may be visually
occluded and thus not seen by the subject. Computing actual visibility requires
more general situation assessment capabilities, and in particular (approximate)
3D models of the surrounding objects so that visibility testing may be
performed, as done in~\cite{sisbot2011situation} for instance. Our experimental
setting did not lead to any specific visual occlusions, and we did not developed
this capability.

Compared to intrusive hardware like head mounted
displays, eye-trackers or wearables for instance, this approach has a clear
advantage of simplicity and integration with robotic systems, but also becomes
accurate enough for general purposes in face-to-face interactions. In addition,
it allows us to model complex environments, handling different number and
positions of participants in the scene.
